---
title: "Unit 4 - 6 Review Starter"

author: "Group 3 - The Best Team"
date: "1 November 2021"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(lubridate)
library(janitor)
```

## Exercises

# Part I - Data Types and Classes

## Exercise 1 - Create some vectors

```{r month-name-vector}
month_name <- c("January", 
                "February",
                "March",
                "April",
                "May",
                "June",
                "July",
                "August",
                "September",
                "October",
                "November",
                "December")
```

#### Member 1

```{r spongebob-vector}
spongebob_characters <- c("spongebob", "patrick", "squidward", "gary", "sandy", "larry", "krabs", "plankton", "dutchman", "karen", "pearl", "neptune")
```

#### Member 2

```{r monthly-season}
season <- c("winter", "winter", "spring", "spring", "spring","summer", "summer", "summer","fall", "fall","winter", "winter")

```


#### Member 3

```{r spooky_vector}
spooky_season <- c(F, F, F, F, F, F, F, F, F, T, F, F)
```

#### Member 4

```{r number-daysinmonth}
n_days <- c(31, 28, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31)
```

#### Member 5

Add your code here.

## Exercise 2 - Combine into a data frame

```{r merge-two-vectors, eval = F}
___ <- tibble::tibble(
  "month_name" = month_name,
  "___" = ___
)
```

#### Member 1

Add your code here.

#### Member 2

Add your code here.

#### Member 3

```{r merge-month-spooky}
month_spooky <- tibble::tibble(
  "month_name" = month_name,
  "spooky_season" = spooky_season
)
```

#### Member 4

Add your code here.

#### Member 5

Add your code here.

## Exercise 3 - Try plotting with `month_name` on the x axis, then recode factors

#### Member 1

Add your code here.

#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.

## Exercise 4 - Join all the data frames, filter randomly, and over-write vector

#### Member 1

Add your code here.

#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.

## Exercise 5 - Try to recombine as a data frame, instead use list

```{r try-merge-vectors, eval = F}
___ <- tibble::tibble(
  "month_name" = month_name,
  "___" = ___
)
```

#### Member 1

Add your code here.

#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.
